\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-20 WOOT/Files/related_work.tex

\subsection{USB Defence Security}
There are already some defenses against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host. At this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui} USB
Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.

@@

>>>>

\subsection{USB Defence Security}
There are already some defenses against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host. At this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.

@@

For those attacks that use the usb cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.

~\ref{table:ccc}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}

		\hline
		\diagbox {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\

		\hline 
		USB condom \cite{Condom}& yes & yes & yes & yes & yes\\
		\hline 
		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& no & ? & no & no & no\\
		\hline 
		TMSUI\cite{yang2015tmsui}& no & yes? & no & no & no\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}& no & yes? & no & no & no\\
		\hline 
		GoodUSB\cite{tian2015defending}& yes & yes & yes? & no & no \\

		\hline
		Neuner et al.\cite{neuner2018usblock}& yes & no & no & no & depends? \\
		\hline
		Meng et al\cite{meng2018252}& no & no & yes & no & ?\\
		\hline
	\end{tabular}
	\linebreak
	\caption{Effectiveness of defense against different attacks}
	\label{table:ccc}
\end{table*}
